
\iffalse
@software{,
  author = {Michael J Marchywka},
  city = {Jasper GA 30143 USA},
  title = { A one-file library for adding machine and human readable bibtex to an article },
abstract={ A simple include file to make bibtex available 
in a document in both machine and human readable format. 
Machine readable is added to extended information 
which can be read with tools such as exiftool ( https://exiftool.org/ ).
While typically not complete at time of pdf creation,
other tools such as toobib can be used to complete the citation
and of course publishers may be able to modify it too as 
more is known. The human readable form need not beincluded
in document types not suited for that but then automated citation
may still be easy.  
See also some exchanges on the Texhax mailing list @tug.org },
institution={},
license={Knowledge sir should be free to all },
publisher={Mike Marchywka},
email={marchywka@hotmail.com},
authorid={orcid.org/0000-0001-9237-455X},
  filename = {mjmaddbib.tex},
  url = {},
  version = {0.0.0},
  date-started = {}
}

<one line to give the program's name and a brief idea of what it does.>


Conceived and written by Mike Marchywka from 2019 to present.
See dates in individual code pieces as they were 
generated from my wizards. 
Copyright (C) <year> <name of author>


This program is free software: you can redistribute it and/or modify it under
the terms of the GNU General Public License as published by the Free Software
Foundation, either version 3 of the License, or (at your option) any later
version.

This program is distributed in the hope that it will be useful, but WITHOUT ANY
WARRANTY; without even the implied warranty of  MERCHANTABILITY or FITNESS FOR
A PARTICULAR PURPOSE. See the GNU General Public License for more details.

You should have received a copy of the GNU General Public License along with
this program.  If not, see <http://www.gnu.org/licenses/>.

   THIS SOFTWARE IS PROVIDED BY THE COPYRIGHT HOLDERS AND CONTRIBUTORS
   "AS IS" AND ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT
   LIMITED TO, THE IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR
   A PARTICULAR PURPOSE ARE DISCLAIMED.  IN NO EVENT SHALL THE COPYRIGHT OWNER OR
   CONTRIBUTORS BE LIABLE FOR ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL,
   EXEMPLARY, OR CONSEQUENTIAL DAMAGES (INCLUDING, BUT NOT LIMITED TO,
   PROCUREMENT OF SUBSTITUTE GOODS OR SERVICES; LOSS OF USE, DATA, OR
   PROFITS; OR BUSINESS INTERRUPTION) HOWEVER CAUSED AND ON ANY THEORY OF
   LIABILITY, WHETHER IN CONTRACT, STRICT LIABILITY, OR TORT (INCLUDING
   NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY OUT OF THE USE OF THIS
   SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF SUCH DAMAGE.


\fi

%\usepackage[pdftex]{graphicx}      % alternative graphics specifications
\usepackage{hyperref}      %


\newcommand{\mjmstartbib}[2]
{
\def\mjmbibentry{@#1\{#2}
\def\mjmbiboneentry{@#1\{#2}
\def\mjmbibpre{x-bib{-}}
\def\mjmday{\day}
%\mjmaddbib{run-day}{\mjmday}
%\mjmaddbib{run-month}{\expandafter\month}
%\mjmaddbib{run-year}{\year}
\mjmaddbib{filename}{\jobname}
\mjmaddbib{run-date}{\today}
}
\newcommand{\mjmbibmunge}[1] {x-bib-#1}

\newcommand{\mjmaddbib}[2]
{
{\hypersetup{pdfinfo={{\mjmbibmunge{#1}}={#2}}}}
\edef\mjmbibentry{\unexpanded\expandafter{\mjmbibentry,}

    #1 =\{#2\} }
%\edef\mjmbiboneentry{\unexpanded\expandafter{\mjmbiboneentry,}
\edef\mjmbiboneentry{\unexpanded\expandafter{\mjmbiboneentry,\linebreak}
#1 =\{#2\}
}

} % mjmaddbib


\newcommand{\mjmshowbib}
{

\mjmbibentry

\}
} % mjmshowbib

\newcommand{\mjmshowbibone}
{
\mjmbiboneentry \}
} % mjmshowbibone

\newcommand{\mjmdonebib}
{

{\hypersetup{pdfinfo={\mjmbibmunge{bibtex}={\mjmshowbibone}}}}

} % mjmdonebib

