\ifdefined\grad
\else
\newcommand{\grad}{\nabla}
\fi
\newcommand{\laplace}{\nabla^{2}}
\newcommand{\mjmdx}[2]{\left(\frac{\partial #1 }{\partial #2} \right) }
\newcommand{\mjmdxop}[2]{\frac{\partial  }{\partial #2}\left( #1 \right) }
\newcommand{\mjmdxdx}[2]{\left(\frac{\partial^{2} #1 }{\partial #2^{2}} \right) }
\newcommand{\mjmdxo}[2]{\frac{\partial #1 }{\partial #2} }
\newcommand{\mjmdxx}[2]{\left(\frac{\partial^{2} #1 }{\partial {#2}^{2}} \right) }
\newcommand{\mjmdxy}[3]{\left(\frac{\partial^{2} #1 }{\partial {#2}\partial{#3}} \right) }
\newcommand{\mjmdxyn}[5]{\left(\frac{\partial^{#1} }{\partial^{#2} {#3}\partial^{#4}{#5}} \right) }
\newcommand{\mjmdsq}[2]{\left(\frac{\partial #1 }{\partial #2} \right) ^{2}}
\newcommand{\mjmupdated}[2]{\p  Updated on $#1$ from source #2 \p }
% see tug mail archives, based on discussion 
%\bool_new:N \l_tmpa_bool
\newif\ifbibstarted
\newif\ifbibnamed
\bibstartedfalse
\bibnamedfalse
\newcommand{\mjmtotalbib}{}
%\def\foo{}
\newcommand{\mjmsummabib}[2]{
%\renewcommand{\mjmtotalbib}{ \mjmtotalbib, #1 = #2 }
%\let\foo{ #1 = #2}
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{mjmaddbib.tex}
\input{mjmlistings.tex}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\newcommand{\mjmaddbib}[2]{\hypersetup{ pdfinfo={ x-bib-#1 = {#2}}}\mjmsummabib{#1}{#2}}

\newcommand{\mjmaddbibonly}[2]{\hypersetup{ pdfinfo={ x-bib-#1 = {#2}}}}
\newcommand{\mjmaddbibe}[2]{\hypersetup{ pdfinfo= x-bib-#1 = #2}}

\newcommand{\mjmtable}[2]{
\begin{table}[H] \centering
\begin{tabular}{#1}
#2
\end{tabular}
\end{table}

}
% for archiving and file list 
% David Carlisle You can use   \textbf{\detokenize{ pmg_ratios.svg}} \IfFileExists{ pmg_ratios.sv}{yes}{no} to make the tokens safe for typesetting in text mode.


\newcommand{\mjmusesitem}[2]{

%\item {\bf $ #1 $  } : #2  % 1 is #1 and 2 is  #2 xxx 
\item {{\detokenize{ #1 } }} : #2  % 1 is #1 and 2 is  #2 xxx 
\IfFileExists{#1}{}{{\bf not found} }

} % mjmuses

\newcommand{\mjmreleasewarning}
{
{\bf This is a draft and has not been peer reviewed or completely proof 
read but released in some state where it seems worthwhile given 
time or other constraints. Typographical errors are quite likely 
particularly in manually entered numbers. This work may 
include  output from software which has not been fully debugged.  
For information only, not for use for any particular purpose see
fuller disclaimers in the text.  Caveat Emptor.}
}

\newcommand{\mjmwarningtoo}
{\bf {This is a draft which may not have been fully proofread and certainly
not peer reviewed. Read the disclaimers and take them seriously.
The reader is assumed familiar with the related literature and
controversial issues. For information and thought only not intended
for any particular purpose. Caveat Emptor  }}

\newcommand{\mjmwarntopic}
{\bf {  This work addresses a controversial topic and likely advances one
or more viewspoints that are not well accepted in an attempt to
resolve confusion.   
The reader is assumed familiar with the related literature and
controversial issues and in any case should seek additional 
input from sources the reader trusts likely with differing opinions. 
For information and thought only not intended
for any particular purpose. Caveat Emptor  }}


\newcommand{\mjmwarnfeed}
{\bf { Note that any item given to a non-human must be checked for safety alone and in combination with other ingredients or medicines  for that animal. Animals including dogs and cats have decreased tolerance for many common ingredients in things meant for human consumption. }}


\newcommand{\mjmwarnme}
{\bf { I am not a veterinarian or a doctor or health care professional
 and this is not particular advice
for any given situation.  Read the disclaimers in the appendicies or text, take them seriously and take prudent steps 
to evaluate this information. 
 }}

\newcommand{\mjmexplainbib}
{{The release may use an experimental bibliography code that
is not designed to achieve a particular format but to
allow multiple links to reference works with modifications
to the query string to allow identification of the citing
work for tracking purposes. This may be useful for a bill-of-materials
and purchases later.
}}





